Gaussian variance estimation in simulated data sets

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

In the first scenario, we simulate data sets with 500 unevenly spaced data
points, and assess accuracy by computing the mean of the squared
errors (MSE) evaluated at 201 equally spaced points.

@@

Compare this table against Table 1 in the paper.

```{r summarize-mse}
cat(sprintf("MSE averaged across %d simulations in Scenario 1,\n",nsim1))
cat(sprintf("and averaged across %d simulations in Scenario 2:\n",nsim2))
mse.table <- rbind(c(mean(mse.mu.uneven.mfvb),mean(mse.sd.uneven.mfvb),
                     mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
                   c(mean(mse.mu.uneven.smash),mean(mse.sd.uneven.smash),
                     mean(mse.mu.even.smash),mean(mse.sd.even.smash)))
rownames(mse.table) <- c("MFVB","SMASH")
colnames(mse.table) <- c("mean","sd","mean","sd")
cat("         Scenario 1      Scenario 2   \n")
cat("      --------------- ----------------\n")
print(mse.table)
```

>>>>

In the first scenario, we simulate data sets with 500 unevenly spaced
data points, and assess accuracy, separately for the mean and variance
estimates) by computing the mean of the squared errors (MSE) evaluated
at 201 equally spaced points.

@@

The following two tables shows the mean squared error (MSE) averaged
over the 100 simulations in each of the scenarios. Compare these
results with Table 1 in the paper.

```{r summarize-mse}
mse.table1 <- rbind(c(mean(mse.mu.uneven.mfvb),mean(mse.sd.uneven.mfvb)),
                    c(mean(mse.mu.uneven.smash),mean(mse.sd.uneven.smash)))
mse.table2 <- rbind(c(mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
                    c(mean(mse.mu.even.smash),mean(mse.sd.even.smash)))
rownames(mse.table1) <- c("MFVB","SMASH")
colnames(mse.table1) <- c("mean","sd")
rownames(mse.table2) <- c("MFVB","SMASH")
colnames(mse.table2) <- c("mean","sd")
cat(sprintf("MSE averaged across %d simulations in Scenario 1:\n",nsim1))
print(mse.table1)
cat(sprintf("and averaged across %d simulations in Scenario 2:\n",nsim2))
print(mse.table2)
```

In Scenario 1, the data are not equally spaced, and the number of data
points is not a power of 2; in this setting, SMASH is more accurate in
estimating both the mean and s.d.

In Scenario 2, the data are equally spaced, and the number of data
points is a power of 2; SMASH again outperforms MFVB in both mean and
s.d. estimation.
